### 2020-02-16 thesis_template/2_RelatedWork/relatedWork.tex
documented

In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
In the CustomerRc and OrderRc struct, all fields take reference counting (Rc<T>). Similaly to the experiment in the last section, 
vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.

@@

Comparing operation on various smart pointer type. 
Rc<T> enables value to have multiple owners, but the value should be immutable. Rc<T> is used in case of single thread. 
When the situation is multi-thread, Arc<T> is used. Arc<T> performs atomic operation, so it is more expensive than Rc<T>. 
When we need to mutate value of Rc<T>, RefCell<T> can be useful. RefCell<T> allow us to have mutiple mutable reference and immutable
of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
That is why RefCell<T> is expensive so that the state of mutable consistency should tracked. 
As Cell<T>, the value is copied in and out of the Cell<T> instead of getting refrence to it. 
In addition, Mutex<T> provides intetior mutability across multi-thread.

Comparison between mutable and immutable tree or graph structure can be checked. 
This is because tree structure requires Rc<T> or Week<T> and in addition RefCell<T> to make it mutable.

@@

If we keep first created owner until the last phase, we can use borrowing to operate.
If we delete first created owner during the operation, we should use Rc<T>.
The question would be, we can use Rc<T> every where?

Smart pointer
\begin{itemize}
    \item Box<T>: Box pointer lets value allocated on heap rather than on the stack.
    \item Rc<T>: Reference counted pointer lets variable take multiple immutable ownership.
\end{itemize}

Interier mutability
    \item Cell<T>: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
    \item RefCell<T>: This support sharing and interier immutability for all types. This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.

@@

LLVM is a library for programmatically creating machine-native code. A develpers can use the API to generate instruction in a format 
called an intermeidiate representation (IR). LLVM can then compile tht IR into a standalone binary, 
perform a JIT (just-in-time) compilation on the code to run in the context of another porgram, such as an interpreter for the language.
LLVM provides a framework API of intermediate representation for common structures of progamming language, such as function, type, struct.
LLVM comes with the portability. It independents of machine architecture.

The most common use of LLVM is for ahead-of-time (AOT) compiler for a language, such as C, C++, Rust. 
However, LLVM can be leveraged with just-in-time (JIT) compiling. 
For example, python is offten used in iterative workflow and rapid development by being a interpreted language.
Using JIT compilation to produce such code complements Python's interactive workflow better thatn ahead-of-time compilation.

LLVM

>>>>

In this experiment, CustomerBorrowed and CustomerRc in figure are used to see difference of dropping time among borrowing and reference counting. 
In the CustomerRc and OrderRc struct, all fields take reference counting (Rc$<$T$>$). Similaly to the experiment in the last section, 
vectors of CustomerRc and CustomerBorrowed are created and droped the elements one by one.

@@

Comparing operation on various smart pointer type. 
Rc<T> enables value to have multiple owners, but the value should be immutable. Rc$<$T$>$ is used in case of single thread. 
When the situation is multi-thread, Arc$<$T$>$ is used. Arc$<$T$>$ performs atomic operation, so it is more expensive than Rc$<$T$>$. 
When we need to mutate value of Rc$<$T$>$, RefCell$<$T$>$ can be useful. RefCell$<$T$>$ allow us to have mutiple mutable reference and immutable
of reference mutable or immutable variable at the same time. When the mutability consistency is voilented, it terminates program during runtime. 
That is why RefCell$<$T$>$ is expensive so that the state of mutable consistency should tracked. 
As Cell$<$T$>$, the value is copied in and out of the Cell$<$T$>$ instead of getting refrence to it. 
In addition, Mutex$<$T$>$ provides intetior mutability across multi-thread.

Comparison between mutable and immutable tree or graph structure can be checked. 
This is because tree structure requires Rc$<$T$>$ or Week$<$T$>$ and in addition RefCell<T> to make it mutable.

@@

If we keep first created owner until the last phase, we can use borrowing to operate.
If we delete first created owner during the operation, we should use Rc$<$T$>$.
The question would be, we can use Rc$<$T$>$ every where?

Smart pointer
\begin{itemize}
    \item Box$<$T$>$: Box pointer lets value allocated on heap rather than on the stack.
    \item Rc$<$T$>$: Reference counted pointer lets variable take multiple immutable ownership.
\end{itemize}

Interier mutability
    \item Cell$<$T$>$: For only Copy type, it allows us to mutate variable, even if it is immutable. Howeever, it does not support sharing the variable so that it returns always copy of the value.
    \item RefCell$<$T$>$: This support sharing and interier immutability for all types. This is done by allowing to get mutable reference from immutable variable and push the error detacting time from compile time to runtime.

@@

\section{Time Line}
\label{sec:history}
\begin{itemize}
    \item End Feb: Finish Experiment for Multithread and Graph
    \item Mid May: ML experiment
    \item End May: Redo experiment with bench mark dataset.
    \item Start April: Finish Writing for first revise.
\end{itemize}

### 2020-02-16 thesis_template/Appendix/Appendix.tex
documented

\section{Memory and Process in Operation Systems}
\label{sec:history}
A process is a section of commutation job. A process can work on a CPU core. We can devide process as well.
Basically, each process does not share thier memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create onther child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
A frame and page are a unit of Separated physical and virtaual memory space in fixed size (4KB or 8KB) respectively.
A process can use as many as pages and correspinding frames obtained by page table matching.

>>>>

\section{Memory and Process in Operation Systems}
\label{sec:history}
A process is a section of computation job. A process can work on a CPU core. We can devide process as well.
Basically, each process does not share thier memory. However, for multiprocessing, we could avoid this restriction.
Processes can be represented as tree structure, because a process may create onther child processes.
Process has 4 states, new, running, waiting, and ready. 
Process is represented in process control block (PCB) with state type, process ID, registers, and so on.
The scheduling for process assigning to CPU core is implemented in queues containing PCB. There are two main queues in this scheduler: 
ready queue and wait queue. The head of process in ready queue is selected for execution and once the process requested I/O request or 
production of child process, the running process will be stored n wait queue. Once the request that the process waiting for end, 
the waiting process will be pushed tail of ready queue.

@@

There are several approaches to deal with this problems. However, we will focus on paging here, which is the most used method OS use to manage memory.
A frame and page are a unit of Separated physical and virtaual memory space in fixed size (4KB or 8KB) respectively.
A process can use as many as pages and correspinding frames obtained by page table matching. This strategy does improve external fragmentation, but not for internal fragmentation.
The smaller size of page has smaller fragmentation, but mapping from page to grame has overhead and also disk I/O is more efficient when the amount of data transfered is larger.

\section{Demand Paging}
\label{sec:history}
A process can have mutiple pages. However, loading entire executable code from sendory storage to memory is not necessarily needed to 
get jobs done. A storategy used in several operating systems is loading only the portion of programs that are needed, demand page.

In the storatege, some pages currently used are in memory and the others are in secondary storage. 
The page table specifies whether pages are valid or invalid, which means are in memory or not. 
Access to a page marked invalid causes page fault and some steps to resolve the error will be required.

The first part of process of demand pageing would be that we check an internal table to check whether the reference is valide or invalid.
If the reference is valid, the process reads the content from the memory. Otherwise, we terminates the process and find the free frame in 
physical memory. Then, we schedule a secondary storage operation to read the desired page into newly allocated frame. 
When the storage complete reading the page, we modify the internal table to indicate the page is now in memory. 
Finally, we restart the instruction that was interrupted.

However, there would be a case where the memory does not have any free frame. In this case, a victim frame that will be replaced with new comming frame should be selected. 
To perform this selection efficiently, a modify bit is tracked for each frame or page. The modify bit represents whether the page is modified since it is loaded from secondary storage. 
If the page or frame is modified, when we swap page we need to update the content in the secondary storage. However, it is not modified, we can simplly delete the frame and replace with new frame.

\section{Copy on Page}
\label{sec:history}
When a parent process creates child process and if these process shares contents on particular page and modify it, 
only the page whitch has the contenst will be copied.
